\documentclass[addpoints]{exam}

\usepackage{amsmath,amssymb, amsthm}
\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\usepackage{forest}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{titling}
\usepackage{wasysym}
\usepackage{mdframed}
\usepackage{arabtex}
\usepackage{utf8}
\setcode{utf8}


% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS 212, Fall 2024}{HW 4: Reductions and Time Complexity}{Fall 2024}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

\newcommand{\classX}[1]{\ensuremath{\text{\textsf{\textbf{#1}}}}} 
\newcommand{\classP}{\classX{P}}
\newcommand{\classNP}{\classX{NP}}
\newcommand{\parkour}{	\diamond_{\text{jump}}}

\boxedpoints
% \printanswers %uncomment this

\title{HW 4: Reductions and Time Complexity\\ \vspace{0.5cm} \Large CS 212 Nature of Computation\\Habib University}
\author{Blingblong} %Enter your team name here
\date{Fall 2024}

\begin{document}
\maketitle

\begin{questions}

    \question[30] Dr. Crowler is getting wary of the friendships developing amongst the students of Duel Academy. After miserably failing to get Jaden Yuki kicked out, in spite Crowler now wants to make every student's life miserable. One idea Crowler had was separate all the friends. The scheme is to reassign student dorms such that if two students are friends they should be assigned a different dorm building. Duel Academy has three dorm building, one for Slifer Red, Obelisk Blue and Ra Yellow. Crowler's secret informant Chazz Princeton has obtained the the information regarding friends groups in Duel Academy. Now the problem is as follows, given the friend pairing of students of Duel Academy, can they be assigned to the three dorm in Duel Academy such that no one is assigned the same dorm as one of their friends. 
    For example, if Jaden is friends with Syrus, Syrus is friends with Chumley, Bastion is friends with Chazz, Alexis is friends with Jaden, Jaden is friends with Chumley, Jaden is friends with Bastion and Alexis is friends with Bastion. Here Jaden can be put in Slifer, Syrus and Bastion can be put in Ra, and Alexis, Chazz and Chumley can be put in Obelisk. For these students its possible to assign them into three dorms such that no two friends are in the same dorm. 
    We formally define this problem as 3-\textsc{dorm-assignment} = $\{\langle F \rangle \in \Sigma^*|$ where $F$ is list of friend pairing of students of Duel Academy and we can assign students in $F$ into three dorms such that no two friends are in the same dorm$\}$.
    Show that for any computational problem $A \subseteq \Sigma^*$, $A$ is decidable iff $A \leq_m 3-\textsc{dorm-assignment}$.
    \begin{solution}
        %enter your solution here
    \end{solution}
    
    \question We have seen in previous weekly challenges that normally we assume that natural numbers are represented as string using the binary basis.That is, a natural number $n$ is represented by the sequence $x_0, x_1, \dots, x_{\log(n)}$ such that $n=\sum_{n}^{i=0}x_i 2^i$. However we could have used other encoding schemes. If $n\in \mathbb{N}$ then for any positive integer $b\geq 2$, the base $b$ representation of $n$, denoted by $\llcorner n \lrcorner_b$ is obtained as follows: First, represent $n$ as a sequence of digits in $\{0,\dots, b-1\}$, and then replace each digit $d \in \{0, \dots, d - 1\}$ by its binary representation. And the unary representation of $n$, denoted by $\llcorner n \lrcorner_1$ unary is the string $1^n$. 
    \begin{parts}
        \part[30] Show that choosing a different base of representation will make no difference to the class $\classP$. That is, show that for every subset $S$ of the natural numbers, if for any $b \in \mathbb{Z}^+$ we define $L^b_S = \{\llcorner n \lrcorner_b | n \in S\}$ then $\forall x\in \mathbb{Z}^+ \setminus \{1\},\;L^x_S \in \classP \iff L^2_S \in \classP$.
        \begin{solution}
            %enter your solution here
        \end{solution}

        \part[20] Consider the language \textsc{factor} = $\{\langle \llcorner n \lrcorner_1, \llcorner k \lrcorner_1\rangle|$ $n$ have a factor smaller than $k$ besides 1$\}$.
        
        Show that choosing the unary representation may make a difference by showing that $\textsc{factor}$ is in $\classP$ but changing base to binary \href{https://en.wikipedia.org/wiki/NP-intermediate}{might} result in a language not being in $\classP$. 
        \begin{solution}
            %enter your solution here
        \end{solution}


    \end{parts} 
      
    \question[20] In parkour civilization everything is decided with parkour, so there is a binary operation on the class of languages known as $\parkour$, where for $A,B \subseteq \Sigma^*$, 
    $$A \parkour B = \{uv| u \in A \text{ and } v \in B\}$$
    A parkour pro asks you to show that $\classNP$ is closed under $\parkour$ for some reason, failing to do so will mean you'd be sent to the parkour prison for 49 years.
    Show that the class $\classNP$ is closed under $\parkour$.
    \begin{solution}
        %enter your solution here
    \end{solution}
    \end{questions}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
